LayeredTypes -- Combining dependent and independent type systems

### 2023-03-15 tex/types2023/types2023.tex
Restructured LaTeX directories
- Now represents individual submissions/styles

 To illustrate this in a small example, consider the program in \Cref{lst:code_before} that reads the text contents of a file and prints it to the console line-by-line. In this short snippet, there are multiple concerns to be addressed. Firstly, one wants to ensure that all function calls are done with variables of the appropriate data types. Secondly, to avoid errors due to an out of bound access, \texttt{get} should only be called with an index that exceeds the list length. Lastly, when working with resources such as a file descriptor it might be useful to track it's state and ensure that it is in a proper (closed) state at the end of program execution. Note that the same standard library functions (\lstinline|createFD|, \lstinline|readLines|, etc...) may be needed in other programs with different type systems requirements.

@@

We evaluated our approach in a prototype language. Users can provide their own implementations for verification layers and define dependencies between them. In \autoref{lst:code_after} we see a set of annotations that can be added to the base code of \autoref{lst:code_before} to tackle the issues described. We define three separate layers \texttt{state}, \texttt{types} and \texttt{liquid}. Internally, the framework will build a dependency graph thus allowing to verify properties independently from one another where appropriate.

@@

%------------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{literature}

%------------------------------------------------------------------------------
\end{document}

>>>>

 To illustrate this in a small example, consider the program in \Cref{lst:code_before} that reads the text contents of a file and prints it to the console line-by-line. In this short snippet, there are multiple concerns to be addressed. Firstly, one wants to ensure that all function calls are done with variables of the appropriate data types. Secondly, to avoid errors due to an out of bound access, \texttt{get} should only be called with an index that does not exceed the list length. Lastly, when working with resources such as a file descriptor it might be useful to track it's state and ensure that it is in a proper (closed) state at the end of program execution. Note that the same standard library functions (\lstinline|createFD|, \lstinline|readLines|, etc...) may be needed in other programs with different type systems requirements.

@@

We evaluated our approach in a prototype language. Users can provide their own implementations for verification layers and define dependencies between them. In \Cref{lst:code_after} we see a set of annotations that can be added to the base code of \Cref{lst:code_before} to tackle the issues described. We define three separate layers \texttt{state}, \texttt{types} and \texttt{liquid}. Internally, the framework will build a dependency graph thus allowing to verify properties independently from one another where appropriate.

@@

\input{../chapters/acknowledgements.tex}

\bibliographystyle{plain}
\bibliography{literature.bib}

\end{document}

%------------------------------------------------------------------------------
